\documentclass[11pt]{article}


\usepackage[sfdefault,semibold,lf]{FiraSans}
\usepackage[a4paper,margin=1.75cm]{geometry}

\usepackage{xcolor}
\definecolor{accent}{HTML}{141E61}

\newcommand{\linkicon}{
  \color{gray}{\footnotesize\raisebox{1pt}{\faIcon{external-link-alt}}}
}

\setcounter{secnumdepth}{0}
\pdfgentounicode=1


%====== LIST FORMATTING ======
\usepackage{enumitem}
\setlist[itemize]{nosep, left=0pt .. 1.5em}
\setlist[enumerate]{left=0pt..1.5em}
\setlist[description]{itemsep=0pt}


%====== TITLE FORMATTING ======
\usepackage{xhfill}
\usepackage{soul}
\newcommand{\midrule}[1]{
  \leavevmode
  \xrfill[.5ex]{1pt}[accent]~\so{#1}~\xrfill[.5ex]{1pt}[accent]
}

\usepackage{titlesec}
\titlespacing{\section}{0pt}{*4}{*1}
\titlespacing{\subsection}{0pt}{*3}{*0}
\titlespacing{\subsubsection}{0pt}{*0}{*0}
\titleformat{\section}{\large\bfseries\uppercase}{}{}{\midrule}
\titleformat*{\subsection}{\large\bfseries\scshape}


%====== CUSTOM COMMANDS ======
\newcommand{\aux}[1]{
  $|$ \space {\normalfont\itshape #1}%
}

\newcommand{\rside}[1]{
  \hfill {\normalfont\color{accent} #1}%
}

%====== FOOTER ======
\usepackage{lastpage}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}

% \fancyfoot[C]{\small\color{gray} Druhan Shah -- Page \thepage\ of \pageref*{LastPage}}
\pagestyle{empty} 
% uncomment previous line to hide page numbering


%====== PACKAGES ======
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage[bookmarks=false,hidelinks]{hyperref}


%====== FINISH PREAMBLE ======

%====== DOCUMENT STARTS HERE ======

\begin{document}

%====== BANNER ======

\begin{center}
  {
    \fontsize{24}{12} 
    \fontseries{heavy}\selectfont
    \color{accent} 
    DRUHAN SHAH
  } \\ \medskip

  {
    \fontsize{10}{8}
    \fontseries{light}\selectfont
    \href{mailto:druhanshah@gmail.com}{{\color{gray}{\faEnvelope}} druhanshah@gmail.com} \quad 
    \href{https://github.com/DruhanShah}{{\color{gray}{\faGithub}} DruhanShah} \quad
    \href{https://www.linkedin.com/in/druhan-shah}{{\color{gray}{\faLinkedin}} druhan-shah} \quad
    \href{https://druhanshah.github.io/}{{\color{gray}{\faLink}} druhanshah.github.io} 
  }
\end{center}

%====== BANNER END ======

\vspace{0.5cm}
  
\noindent March 16, 2026
\vspace{0.75cm}

\noindent The Hiring Manager, \\
Jane Street Asia Limited \\
10th Floor, Chater House \\
8 Connaught Rd. Central \\
Central, Hong Kong \\
\vspace{0.75cm}

\noindent Dear Hiring Manager,

\paragraph{} I'm Druhan, an undergradute student. It is with great enthusiasm that I am applying for the post of Software Enginnering Intern at Jane Street. When I saw your opening for internships, which was shared by my university along with information about the FTTP, I knew my background in mathematics and computer science would be a solid contributor. I've always looked up to Jane Street as a company that values rigour, depth, and problem-solving ability in abstract theoretical sciences, and would love an opportunity to contribute to it.

\paragraph{} From a young age, I've been interested in mathematics, computer science and linguistics, having qualified for the training camps for the International Olympiads for Mathematics and Linguistics. I've taken part in several similar international contests in the three fields. I've held the position of Coordinator for my university's Theory Group, which is a student club aimed at demystifying and sharing knowledge of more theoretical and abstract aspects of any scientific field. In this role, I was part of organizing the university's first Integration Bee (inspired by the eponymous contest by MIT), and conducted several talks on abstract algebra.

\paragraph{} I've implemented several software projects during my time in university, including contributing to open-source projects aimed at helping the university community in tangible ways. One such project I've contributed to is a MAS-based documentation generator that uses LSPs to query large student-written codebases. This project was also the winner of the HackIIIT Hackathon 2024. I currently specialize in Deep Learning and Interpretability, as I'm currently working on multiple research projects in the field.

\paragraph{} Initially, I felt that my skills and interests were quite disjoint, seemingly tearing me in two directions. I now see that Jane Street would be the perfect place for me to make good use of every single one of them. I've heard quite a lot about Jane Street's emphasis on mathematics and problem-solving, some from online content creators like 3Blue1Brown and Stand Up Maths. I've also heard a lot about Jane Street's use of Machine Learning models to enable better quantitative trading methods, which is where I believe my skill with Interpretability will be useful.

\paragraph{} I'd greatly appreciate the opportunity to discuss how I can contribute to Jane Street. Thank you for your time, I look forward to hearing from you.

\paragraph{} Best regards,

Druhan Rajiv Shah

\end{document}
