\documentclass[11pt]{article}


\usepackage[sfdefault,semibold,lf]{FiraSans}
\usepackage[a4paper,margin=1.75cm]{geometry}

\usepackage{xcolor}
\definecolor{accent}{HTML}{141E61}

\newcommand{\linkicon}{
  \color{gray}{\footnotesize\raisebox{1pt}{\faIcon{external-link-alt}}}
}

\setcounter{secnumdepth}{0}
\pdfgentounicode=1


%====== LIST FORMATTING ======
\usepackage{enumitem}
\setlist[itemize]{nosep, left=0pt .. 1.5em}
\setlist[enumerate]{left=0pt..1.5em}
\setlist[description]{itemsep=0pt}


%====== TITLE FORMATTING ======
\usepackage{xhfill}
\usepackage{soul}
\newcommand{\midrule}[1]{
  \leavevmode
  \xrfill[.5ex]{1pt}[accent]~\so{#1}~\xrfill[.5ex]{1pt}[accent]
}

\usepackage{titlesec}
\titlespacing{\section}{0pt}{*4}{*1}
\titlespacing{\subsection}{0pt}{*3}{*0}
\titlespacing{\subsubsection}{0pt}{*0}{*0}
\titleformat{\section}{\large\bfseries\uppercase}{}{}{\midrule}
\titleformat*{\subsection}{\large\bfseries\scshape}


%====== CUSTOM COMMANDS ======
\newcommand{\aux}[1]{
  $|$ \space {\normalfont\itshape #1}%
}

\newcommand{\rside}[1]{
  \hfill {\normalfont\color{accent} #1}%
}

%====== FOOTER ======
\usepackage{lastpage}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}

% Replace 'Star Rover' with your name in next line
\fancyfoot[C]{\small\color{gray} Druhan Shah -- Page \thepage\ of \pageref*{LastPage}}
% \pagestyle{empty} 
% uncomment previous line to hide page numbering


%====== PACKAGES ======
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage[bookmarks=false,hidelinks]{hyperref}


%====== FINISH PREAMBLE ======

%====== DOCUMENT STARTS HERE ======

\begin{document}

%====== BANNER ======

\begin{center}
  {
    \fontsize{24}{12} 
    \fontseries{heavy}\selectfont
    \color{accent} 
    DRUHAN SHAH % YOUR NAME HERE
  } \\ \medskip

  {
    \fontsize{10}{8}
    \fontseries{light}\selectfont
    \href{mailto:druhanshah@gmail.com}{{\color{gray}{\faEnvelope}} druhanshah@gmail.com} \quad 
    \href{https://github.com/DruhanShah}{{\color{gray}{\faGithub}} DruhanShah} \quad
    \href{https://www.linkedin.com/in/druhan-shah}{{\color{gray}{\faLinkedin}} druhan-shah} \quad
    \href{https://druhanshah.github.io/}{{\color{gray}{\faLink}} druhanshah.github.io} 
  }
\end{center}

%====== BANNER END ======


\section{Education}
%==========
\subsection{IIIT Hyderabad \aux{B.Tech. (Hons) in Computer Science} \rside{2021 --}}
  \begin{itemize}
  \item Relevant courses: Advanced NLP, Operating Systems and Networks
  \item Dean's Merit List 2022
\end{itemize}

\subsection{IIIT Hyderabad \aux{M.S by Research in Computational Linguistics} \rside{2021 --}}
  \begin{itemize}
  \item Relevant courses: Applications of Language Models, Information Retrieval and Extraction
\end{itemize}


\section{Experience}
%==========
\subsection{Language Technologies Research Centre}
\subsubsection{Student Researcher \rside{May 2023 --}}
\begin{itemize}
  \item Explored Interpretability methods for neural Language Models.
  \item Studying the use of Formal Languages to quantify the expressivity of Transformers.
\end{itemize}

\subsection{IIIT Hyderabad}
\subsubsection{Head Teaching Assistant \rside{Jan 2026 --}}
\begin{itemize}
  \item Led teams of teaching assistants for the Introduction to NLP and Advanced NLP courses.
  \item Responsible for division of tasks across the team, and contributing to course planning.
  \item Set and evaluated quizzes and homework assignments, and conducted tutorials.
\end{itemize}


\section{Volunteering}
\subsection{Panini Linguistics Olympiad}
\subsubsection{Problem Committee Member \rside{Jan 2024 --}}
\begin{itemize}
\item Contributed problems for the national and pre-national stages of the Panini Linguistics Olympiad.
\item Tested and critiqued problems for the national stage and the training camp stages.
\end{itemize}
\subsubsection{Teaching Assistant \rside{Apr 2023 -- May 2023}}
\begin{itemize}
\item Conducted tutorial sessions, and trained selected students to represent India at the IOL.
\item Evaluated submissions for the Indian participants of the Asia-Pacific Linguistics Olympiad.
\end{itemize}

\subsection{Theory Group, IIIT Hyderabad}
\subsubsection{Coordinator and Moderator \rside{Oct 2022 -- Mar 2024}}
\begin{itemize}
\item Led a team of Moderators to conduct and direct weekly seminars on Mathematics, Theoretical Computer Science, Philosophy and Music Theory.
\item Organized club logistics and budgets for the year 2023-24.
\end{itemize}


\section{Projects}
%=================
\subsection{Firefly \aux{\href{https://github.com/WackIIIT/Firefly}{Project Link \linkicon}} \rside{Mar 2025}}
A Multi-agent documentation and code generator using the Language Server Protocol.

\subsection{Essay Evaluation as Evidence-NLI \rside{Jan 2026 -- May 2026}}
A novel formulation of the Essay Evaluation task as a variant of NL, and a novel GNN and SSM-based approach evaluated against State-of-the-Art methods.

\subsection{Indic Morpho-semantic Circuits \aux{\href{https://github.com/DruhanShah/indic-morpho-semantic-circuits}{Project Link \linkicon}} \rside{Aug 2025 -- Dec 2025}}
Extracting circuits from monolingual generative language models using known Mechanistic Interpretability methods, and analysing them with an emphasis on Dependency and Paninian Grammars.


\section{Awards and Contests}
%===============
\begin{description}
  \item [2025] HackIIIT, DeccanCTF
  \item [2024] Amazon ML Challenge
  \item [2022] Dean's Merit List
  \item [2021] Training Camps for the IMO and IOL
\end{description}


\section{Skills}
%===============
\begin{description}
  \item[Programming] Python, C/C++, JavaScript, Rust, Lisps
  \item[Interests] Abstract Algebra, Historical Linguistics, Music Theory, Free Software
\end{description}


\end{document}
